---
title: "Assignment_4"
author: "Swathi Suragowni Ravindranath"
date: '2022-03-21'
output:
  pdf_document: default
  html_document: default
---

```{r}

library(factoextra)
library(ggplot2)
Pharmaanalyst<-read.csv("C:/Users/ravin/Downloads/Pharmaceuticals.csv")
summary(Pharmaanalyst)
```
#a)Use only the numerical variables (1 to 9) to cluster the 21 firms. Justify the various choices made in conducting the cluster analysis, such as weights for different variables, the specific clustering algorithm(s) used, the number of clusters formed, and so on.
Prior to clustering data, remove the missing data and rescale variables for comparability.
```{r}
x <- na.omit(Pharmaanalyst) #gives the data after removing the incomplete cases.
x
```
collect only the quantitative variables(1-9) to cluster the 21 firms
```{r}
row.names(x)<- x[,1]
Pharma1<- x[,3:11]
head(Pharma1)
```
Scale all the quantitative variables in the dataframe
```{r}
Pharma2<-scale(Pharma1)
head(Pharma2)
```
To determine the no of clusters to do the cluster analysis using Elbow Method
```{r}
fviz_nbclust(Pharma2, kmeans, method = "wss") + labs(subtitle = "Elbow Method")
```
Silhouette method for determining no of clusters
```{r}
fviz_nbclust(Pharma2, kmeans, method = "silhouette")+ labs(subtitle = "Silhouette Method")
```
from the above plots, it is clear that the no of clusters are 5 and they are enough to show the variations that are present in the data
```{r}
set.seed(120)
k5<- kmeans(Pharma2,centers=5,nstart = 25) 
#Visualize the output
k5$centers  #centroids
fviz_cluster(k5,data = Pharma2) # to Visualize the clusters
k5
distance<- dist(Pharma2, method = "euclidean")
fviz_dist(distance)
```
K-Means Cluster Analysis- Fit the data with 5 clusters

```{r}
fit<-kmeans(Pharma2,5)
```

Finding the mean value of all quantitative variables for each cluster

```{r}
aggregate(Pharma2,by=list(fit$cluster),FUN=mean)
```
```{r}
Pharma3<-data.frame(Pharma2,fit$cluster)
Pharma3
View(Pharma3)
```
To view the cluster plot
```{r}
library(cluster)
clusplot(Pharma2,fit$cluster,color = TRUE,shade = TRUE,labels = 2,lines = 0)
```

#b)Interpret the clusters with respect to the numerical variables used in forming the clusters.

By observing the mean values of all quantitative variables for each cluster

Cluster 1 - BAY, CHTT, IVX

Cluster 2 - ABT, AZN, BMY, LLY, NVS, SGP,WYE

Cluster 3 - ELN, MRX

Cluster 4 - JNJ, MRK, PFE, GSK

Cluster 5 - AGN, AHM, AVE, PHA, WPI

Cluster 1 has highest Beta , Leverage and lowest Market_Cap, ROE, ROA, Leverage, Rev_Growth, Net_Profit_Margin
Cluster 2 has highest Net_Profit_Margin and lowest Beta.
Cluster 3 has highest Rev_Growth and lowest PE_Ratio, Asset_Turnover.
Cluster 4 has highest Market_Cap, ROE, ROA,Asset_Turnover 
Cluster 5 has highest PE_Ratio.

#c)Is there a pattern in the clusters with respect to the numerical variables (10 to 12)? (those not used in forming the clusters)

There is a pattern in the clusters with respect to Media recommendation variable.

Cluster 1 with highest Beta, highest Leverage has mostly Moderate Buy Recommendation.

Cluster 2 with highest Net_Profit_Margin has mostly Hold Recommendation

Cluster 3 with lowest PE_Ratio  and lowest Asset_Turnover has Hold Recommendation

Cluster 4 with highest Market_Cap, highest ROE, highest ROA, highest Asset_Turnover has equal Hold and Moderate Buy Recommendation

Cluster 5 with highest PE_Ratio  has the Strong Buy Recommendation, because high PE_Ratio indicates the company is growing fast.

Could see a pattern among the clusters with respect to variables(10 to 12)

Clusters 1,4 has mostly Moderate Buy Recommendation

Clusters 2,3,4 has Hold Recommendation
                                                      
#d)Provide an appropriate name for each cluster using any or all of the variables in the dataset.

Cluster1 - high Beta, Leverage cluster (or) Buy Cluster. 

Cluster2 - high Net_Profit_Margin cluster (or) high hold cluster.

Cluster3 - Low PE_Ratio, Asset_Turnover cluster (or) hold cluster.

Cluster4 - Moderate Buy cluster

Cluster5 - high PE_Ratio cluster (or) high Buy cluster.
